The hydra and the rooster

### 2020-07-21 latex/chapter-ordinals.tex
various renamings: not yet corrected in latex

\begin{Coqsrc}
Class OrdinalNotation {A:Type}{lt: relation A}(sto:StrictOrder lt)
      (compare : A -> A -> comparison)  :=
  {   wf : well_founded lt;
      compare_correct :
         forall alpha beta:A,
          CompareSpec (alpha=beta) (lt alpha beta) (lt beta alpha)
                                   (compare alpha beta);
  }. 
\end{Coqsrc}

>>>>

\begin{Coqsrc}
Class OrdinalNotation {A:Type}{lt: relation A}(sto:StrictOrder lt)
      (compare : A -> A -> comparison)  :=
  {   wf : well_founded lt;
      compare_correct :
         forall alpha beta:A,
          CompareSpec (alpha=beta) (lt alpha beta) (lt beta alpha)
                                   (compare alpha beta);
  }.

Definition on_t  {A:Type}{lt: relation A}
            {compare : A -> A -> comparison}
            {on : OrdinalNotation lt compare} := A.

Definition on_compare {A:Type}{lt: relation A}
            {compare : A -> A -> comparison}
            {on : OrdinalNotation lt compare} := compare.

Definition on_lt {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : OrdinalNotation lt compare} := lt.

Definition on_le  {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : OrdinalNotation lt compare} :=
  clos_refl _ on_lt.
